UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-08-07 main.tex
:pencil: Update contributions

	% TODO You need to explain the key principle and benefits of backscatter, then symbiotic radio, then RIS. Then you need to explain about the apparent differences and similarities between those techniques. Then metascatter concept will appear.

@@

	% Specifically, a dedicated emitter generates a sinusoidal carrier at reserved frequency, and \gls{rfid} tags reports their identifier to a nearby \gls{rfid} reader.

@@

	Ideal joint \gls{ml} decoding achieves optimal performance with prohibitive computational complexity \cite{Yang2018,Zhang2022}.

@@

	This motivated \cite{Long2020a,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to first decode the primary link, perform \gls{sic}, then decode the backscatter link.

@@

	% \cite{Xu2021a} proposed a backscatter \gls{noma}-based \gls{sr} by extending \gls{sic} to multi-node scenario, where the decoding order depends on backscatter signal strength.

@@

	% Although energy efficiency can be enhanced by transmission time and reflection ratio design, it requires regular feedback to passive nodes and incurs high coordination cost.

@@

	% \cite{Zhou2019a} also explored the asymptotic impact of transmit/receive antenna and backscatter symbol period on the ergodic rate of primary and backscatter links.
	% For a \gls{mimo} \gls{sr} system with a multi-antenna backscatter node, \cite{Wu2021a} proposed a beamforming design to maximize the backscatter rate while guaranteeing the primary performance.
	% However, those paper only considered one backscatter node and backscatter multiple access remains an open issue.
	% In \cite{Xu2021a}, a \gls{noma}-based \gls{sr} was proposed and receive combining was investigated when \gls{sic} order follows equivalent channel strength.
	% A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, where transmit power, reflection efficiency, and time allocation were jointly optimized to maximize energy efficiency.
	% To reduce coordination between passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.

	On the other hand, \gls{ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference.
	% Compared with backscatter nodes of \gls{bc} and \gls{sr}, the reflection pattern of \gls{ris} elements are deterministic and priorly known at transmitter and receiver.
	Compared with backscatter nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
	This motivated the use of fixed reflection coefficients during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients over different time slots within channel block, was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	Dynamic \gls{ris} provides artificial channel diversity and flexible resource allocation, but misses the opportunity to encode its own message.
	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary passive beamforming device to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
	It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} also as an information source to combine passive beamforming and backscatter modulation in the overall reflection pattern.
	% In particular, \emph{symbol level precoding} maps backscatter symbols to optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
	In particular, \emph{symbol level precoding} maps backscatter symbols to \gls{ris} coefficient sets optimized for detection \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
	% However, those \gls{ris}-empowered \gls{bc} and \gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.
	However, those \gls{ris}-empowered \gls{bc} and \gls{sr} designs involve advanced hardware architecture and high optimization complexity.

	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.

	To the best of our knowledge, all existing \gls{sr} literatures assumed backscatter modulation employs either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a} or finite equiprobable inputs \cite{Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022,Hu2021a}.
	The former is impractical for passive nodes with constrained number of states, while the latter does not fully exploit \gls{csi} to boost achievable backscatter rate.
	Besides, most relevant designs \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Xu2020b,Hua2022} were built over ideal \gls{ml} or \gls{sic} receiver.
	However, the advantage of \gls{sic} is questionable because 1) it requires non-coherent primary encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver, 2) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 3) the backscatter symbol period is typically much longer due to physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
	Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{ris}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

@@

	\emph{Notations:} Scalars, vectors and matrices are respectively denoted by italic, bold lower-case, and bold upper-case letters.
	$j$ represents the imaginary unit.
	% $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
	% $\boldsymbol{I}$ represents the identity matrix.
	% $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ respectively denote the space of real nonnegative and complex $x \times y$ matrices.
	$\Delta^n = \left\{ (p_0,\dots,p_n) \in \mathbb{R}_+^{n+1}|\sum_{i=0}^n t_i = 1 \right\}$ denotes the standard $n$-simplex.
	% $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ respectively represent the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ respectively denote the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
	% $\odot$ denotes the Hadamard product.
	% $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
	% $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
	% $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity).
	The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
	$\sim$ means ``distributed as''.
	$(\cdot)^{(i)}$ represents the $i$-th iterated value and $(\cdot)^{\star}$ represents the end solution.
\end{section}

>>>>

@@

	% ? Specifically, a dedicated emitter generates a sinusoidal carrier at reserved frequency, and \gls{rfid} tags reports their identifier to a nearby \gls{rfid} reader.

@@

	Ideal joint \gls{ml} decoding achieves optimal performance with prohibitive computational complexity \cite{Yang2018,Liang2020,Zhang2022}.

@@

	This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to first decode the primary link, perform \gls{sic}, then decode the backscatter link.

@@

@@

@@

	On the other hand, \gls{ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
	The scattered signals contain no additional information, but adds constructively or destructively with the direct component to enhance desired signal or suppress interference.
	Compared with backscatter nodes of \gls{bc}/\gls{sr}, \gls{ris} elements employ deterministic reflection pattern priorly known at transmitter and receiver.
	This motivated the use of fixed reflection coefficients during each channel block to improve communication, sensing, and power performances \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	The concept of dynamic \gls{ris}, namely choosing independent reflection coefficients over different time slots within channel block, was first considered for resource blocks of \gls{ofdm} systems, then extended to power and information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	Dynamic \gls{ris} provides artificial channel diversity and flexible resource allocation, but misses the opportunity to encode its own message.
	From an information-theoretic perspective, \cite{Karasik2020} reported using \gls{ris} as an auxiliary passive beamforming device to maximize the \gls{snr} is generally rate-suboptimal for finite input constellations.
	Instead, joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided channel, and layered encoding with \gls{sic} decoding (i.e., \gls{sic}-based \gls{sr}) can outperform pure passive beamforming at high \gls{snr}.
	It inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to employ \gls{ris} also as an information source to combine passive beamforming and backscatter modulation in the overall reflection pattern.
	In particular, \emph{symbol level precoding} maps backscatter symbols to \gls{ris} coefficient sets optimized for detection \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes information-bearing symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} divides \gls{ris} into reflection elements for passive beamforming and information elements for on-off modulation \cite{Hu2021a}.
	However, those \gls{ris}-empowered \gls{bc}/\gls{sr} designs involve advanced hardware architecture, high optimization complexity, and additional control overhead.

	To the best of our knowledge, all relevant literatures assumed either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} at backscatter information sources.
	The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
	In this paper, we introduce the concept of UniScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and backscatter detector design.
	The contributions of this paper are summarized as follows.

	\emph{First,} we propose the UniScatter node that adapt input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation and passive beamforming.
	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distirbution boils down to equiprobable and degenerate, respectively.
	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, it requires regular coordination with passive nodes, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can achieve higher instantaneous backscatter rate.

	\emph{Second,} we propose a novel backscatter re

	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
	Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.

	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{ris}.
	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.

	nodes that adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.

	% Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{ris}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	% The contributions of this paper is summarized as follows.

@@

	\emph{Notations:} Scalars, vectors and matrices are respectively denoted by italic, bold lower-case, and bold upper-case letters.
	$j$ represents the imaginary unit.
	% $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
	% $\boldsymbol{I}$ represents the identity matrix.
	% $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ respectively denote the space of real nonnegative and complex $x \times y$ matrices.
	% $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ respectively represent the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ respectively denote the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
	% $\odot$ denotes the Hadamard product.
	% $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
	% $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
	% $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity).
	The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
	$\sim$ means ``distributed as''.
	$(\cdot)^{(i)}$ represents the $i$-th iterated value and $(\cdot)^{\star}$ represents the end solution.
\end{section}
